### 2021-09-02 analysis/analysis.Rmd
removed p from optimisation to focus on others, need to optimise p after

plots_data <- purrr::map(
  sites,
  ~ {
    subdat <- data %>% dplyr::filter(.data$site == .x)
    df <- readRDS(paste0(path, "/", .x, ".rds"))[-3]
    results_tibble <- make_results_tibble(df) %>%
      rowwise() %>%
      mutate(
        ks_p = calc_ks_boot(
          subdat$foraging_distance, c(p, ls, ln, qn, a),
          data_name, TRUE
        ),
        ks_d = calc_ks(
          subdat$foraging_distance, c(p, ls, ln, qn, a),
          data_name, TRUE
        ),
        site = .x
      ) %>%
      select(
        site,
        everything()
      )
    print(paste(.x, length(subdat$foraging_distance)))
    if (.x == "STU") {
      ret <- list(
        site_name = list(
          results_tibble,
          make_full_plot(
            subdat$foraging_distance, df,
            subplot_coords = c(0.5, 6, -6, -2.5)
          )
        )
      )
    } else {
      ret <- list(
        site_name = list(
          results_tibble,
          make_full_plot(subdat$foraging_distance, df)
        )
      )
    }
    return(ret)
  }
)
```

>>>>

plots_data <- purrr::map(
  sites,
  ~ {
    subdat <- data %>% dplyr::filter(.data$site == .x)
    df <- readRDS(paste0(path, "/", .x, ".rds"))[-3]
    results_tibble <- make_results_tibble(df) %>%
      rowwise() %>%
      mutate(
        ks_p = calc_ks_boot(
          subdat$foraging_distance, c(p, ls, ln, qn, a),
          data_name, TRUE
        ),
        ks_d = calc_ks(
          subdat$foraging_distance, c(p, ls, ln, qn, a),
          data_name, TRUE
        ),
        site = .x
      ) %>%
      select(
        site,
        everything()
      )
    print(paste(.x, length(subdat$foraging_distance)))
    if (.x == "STU") {
      ret <- list(
        site_name = list(
          results_tibble,
          make_full_plot(
            subdat$foraging_distance, df,
            subplot_coords = c(0.5, 6, -6, -2.5)
          )
        )
      )
    } else if (.x == "CAD") {
      ret <- list(
        site_name = list(
          results_tibble,
          make_full_plot(
            subdat$foraging_distance, df,
            subplot_coords = c(0.8, 2.2, -5, -2)
          )
        )
      )
    } else {
      ret <- list(
        site_name = list(
          results_tibble,
          make_full_plot(subdat$foraging_distance, df)
        )
      )
    }
    return(ret)
  }
)
```

### 2021-09-02 analysis/proportions-of-scouts.Rmd
removed p from optimisation to focus on others, need to optimise p after

@@

>>>>

# keep only best fitting model
model_results <- model_results %>% group_by(site) %>% top_n(-1, AIC)

@@

```{r}
# bootstrapped mean / median
boot.median <- function(data, n = 10000) {
  resamples <- purrr::map_dbl(
    seq_len(n),
    ~ {
      median(sample(data$p, replace = TRUE))
    }
  )
  std.err <- sqrt(var(resamples))
  return(list(std.err = std.err, medians = resamples))
}

urban.boot <- model_results_pscouts %>%
  filter(LU == "Urban") %>%
  select(p) %>%
  boot.median()

hist(urban.boot$medians)

rural.boot <- model_results_pscouts %>%
  filter(LU == "Rural") %>%
  select(p) %>%
  boot.median()

hist(rural.boot$medians)

# beta regression
library(betareg)

model_results_pscouts

betamod <- betareg(p ~ LU, data = model_results_pscouts)
summary(betamod)
model_results_pscouts$predbeta = predict(betamod, interval = "confidence")

ggplot(data = model_results_pscouts, aes(x = LU, y = p)) +
  geom_point() +
  geom_point(aes(y = predbeta, color = LU))

The above plot (code to make the beta plot) fits a beta regression. The beta regression is to be used when the predictor variables are proprtions. Whilst there is no difference between the proportion of scouts in urban and rural landscapes, there is a much tighter spread in the urban colonies than the rural colonies.
